Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
removing placeholder package.

\noindent Note that the {\tt placeholders} library provides better
keywords such as {\tt notImplemented} and {\tt todo}, which tells
source locations when executed.
\begin{quote}
    sol: @kazu Would it be fine with you to remove the reference to
    placeholders?

    \begin{itemize}
        \item Do we need it to make our point?
        \item It requires template-haskell and additional import, and
            is thus not very practical.
    \end{itemize}
\end{quote}

Next we write user documentation in Haddock markup:

>>>>

\noindent Next we write user documentation in Haddock markup:
